\sys: Automated Data-Parallel Shell Processing

### 2020-04-16 pldi/draft.tex
Some notes on paper draft

>>>>

\kk{Maximum scaleup for both diff and set-diff is around half because
  they already have two sorts running in parallel (as diff, and comm
  take two inputs).}

\TODO{Explain the plots with eager/no-eager as follows. Say that we
  initially decided to only make an eager version of cat (to allow for
  parallelism). However, we saw that results are still not good, so we
  resorted to making a proper generic eager node that can be put
  anywhere in the graph and that eagerly consumes its input. The above
  results show the improvement with it. Rerun them with eager only
  before cat in the no eager cases to showcase the above
  results. (Maybe) we need to mention that eager has disk usage
  overhead that is linear to the size of the pipeline and the size of
  the input.}
